---
title: "Developing Data Products Project"
author: "Vebash Naidoo"
date: "February 10, 2018"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Movie Data
The Movie Data was downloaded from a course I did on DataCamp. The shiny app has 2 tabs and was done as an interactive R Markdown document with Shiny components embedded in the R Markdown!

* On tab 1 is an interactive plot where the x-axis, y-axis and colour of data points may be amended by the choices made by the user.
* On tab 2 is a data table where the genre(s) selected in the Genre text box are displayed on a table. The "muliple = T" in select input allows for the selection to take multiple entries. It's very nifty!

```{r, echo = F, warning= F, message=F}
suppressPackageStartupMessages(library(tidyverse))
suppressPackageStartupMessages(library(plotly))
suppressPackageStartupMessages(library(ggplot2))
suppressPackageStartupMessages(library(lubridate))

# Import movie data 
load("./movies.Rdata")
```

## Glimpse at the data

```{r, echo = F, warning= F, comment=""}
# View the first 5 rows of movies
glimpse(movies)
```

## Genres in the data

The Genres is the main element of the data table on tab 2.
```{r, echo = F, warning= F, error= F, message=F}

p<- ggplot(movies, aes(x = genre)) + geom_bar() + theme(axis.text.x = element_text(angle = 90, hjust = 1))

(gg <- ggplotly(p))

```

***
Please run the app at https://vebash.shinyapps.io/Dev_Data_Products_W4/ 

... hope you enjoy!

Thank you for reviewing!

